\textsc{Second-order state-constraint Hamilton-Jacobi equations}

### 2021-04-06 Drafts and notes/Attempts/Old_draft_04.tex
Major change

\begin{proof} For $\delta>0$, let us define $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\Omega) < \delta\}$ $\textcolor{orange}{(\mathrm{dist}(x,\partial \Omega) > \delta)}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: \mathrm{dist}(x,\overline{\Omega}) < \delta\}$. 
\begin{figure}[ht]
    \centering
    %\incfig{Domains}
    \def\svgwidth{0.47\columnwidth}
    \import{./figs/}{Domains.pdf_tex}
    \caption{The domain $\Omega$ variations $\Omega_\delta, \Omega^\delta$.}
    \label{fig:Domains}
\end{figure}
We consider $\delta$ small enough so that the distance function $x\mapsto \mathrm{dist}(x,\partial \Omega)$ is $\mathrm{C}^2$ in the strip $\Omega^\delta\backslash \overline{\Omega}_\delta$, we recall that $|D d(x)| = 1$ in that region. We extend the signed distance function into a $\mathrm{C}^2(\mathbb{R}^n)$ function, denoted by $d(x)$ such that 
\begin{equation*}
    \begin{cases}
    d(x)\geq 0\;\text{for}\;x\in\Omega\;\text{with}\;d(x) = +\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega\backslash \Omega_\delta,\\
    d(x)\leq 0\;\text{for}\;x\notin \Omega\;\text{with}\;d(x) = -\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega^\delta\backslash \Omega.
    \end{cases}
\end{equation*}
We can choose $d(\cdot)$ so that $\Omega_\delta = \{x\in \mathbb{R}^n: d(x)-\delta >0 \}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: d(x) +\delta>0\}$.

@@

\begin{lem}\label{lem:supersln} For each $\eta>0$ there exists $M_\eta > 0$ such that 
\begin{equation*}
    \overline{w}_{\eta,\delta}(x) \textcolor{orange}{(\underline{w}_{\eta, \delta})} = \frac{C_\varepsilon-\eta}{(d(x)+\delta)^\alpha} -\frac{M_\eta}{\lambda}, \qquad x\in \Omega^\delta 
\end{equation*}
is a supersolution $\textcolor{orange}{(subsolution)}$ of \eqref{eq:PDEeps} in $\Omega^\delta$.
\end{lem}

@@

\begin{prop}\label{pro:minimalsol} There exists a minimal solution $\underline{u}\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps} such that $v\geq \underline{u}$ for any other solution $v\in \mathrm{C}^2(\Omega)$ solving \eqref{eq:PDEeps}.
\end{prop}
\begin{proof} Let $w_{\eta,\delta}\in \mathrm{C}^2(\Omega)$ solves
    \begin{equation}\label{e:w_def}
    \begin{cases}
        \mathcal{L}\left[w_{\eta,\delta}\right] = 0 &\qquad\text{in}\;\Omega,\\
        \qquad w_{\eta,\delta} = \underline{w}_{\eta,\delta} &\qquad\text{on}\;\partial\Omega.
    \end{cases}
    \end{equation}
    Fix $\eta>0$, as $\delta\to 0$ the value of $\underline{w}_{\eta,\delta}$ blows up on the boundary, therefore by comparison principle we have $\delta_1 \leq  \delta_2$ implies $w_{\eta,\delta_1}\geq  w_{\eta,\delta_2}$ on $\overline{\Omega}$.

@@

\section{Rate of convergence via Doubling variables - a toy case}

@@

    \Phi^{\sigma}(x,y) =  u^\varepsilon(x) - u_\delta(y) - \frac{L_0|x-y|^2}{\sigma}- \frac{C_\varepsilon}{d(x)^{\alpha+\beta}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}_\delta

@@

where $L_0$ is the Lipschitz constant of $u^0$ and $u_\delta\in \mathrm{C}(\overline{\Omega}_\delta)$ is the state-constraint solution to

@@

\color{blue}
\textcolor{blue}{\textbf{The next questions and tasks:}}
\begin{enumerate}
    \item Check all the constants, make sure things are correct!
    \item It seems that $\sqrt{\varepsilon}$ is the best using this method. Now we can improve this by either:
    \begin{itemize}
        \item[(a)] Make the boundary layer to $\sqrt{\varepsilon}$ only, instead of $2\sqrt{\varepsilon}$.
        \item[(b)] \textcolor{red}{\textbf{Important.}} Generalize this to more general domain, possibly star-shaped domains where we can do scaling is fine (just my guess).
    \end{itemize}
    \item Other formulations of the doubling variable method here, for example, in the first step, it seems that making $\Phi^\sigma(x,y)\to  -\infty$ as $x\to \partial\Omega$ is "\emph{too wasteful}". One may need only to do something like
        \Phi^\sigma(x,y) < \Phi^\sigma(0,0) \qquad\text{if}\qquad d(x) < \;\text{something close to the boundary}.
    Can we improve that to get a better rate? My guess is not even if we can improve this, since the dominating term coming from $\varepsilon^\gamma$ and $\varepsilon^{1-\gamma}$ later. Nevertheless, it maybe still interesting to see why and how the \emph{wasteful} formulation here can be improved.
    \item \textcolor{red}{\textbf{Important.}} Using nonlinear adjoint method.
    \item Now once we have some rate, can we do bootstrap to improve it as we discussed earlier (the simple ideas, ...)?
    \item \textcolor{red}{\textbf{Important.}} Can we find an example where $|u^\varepsilon - u^0| = \mathcal{O}(1)$ in the strip where $0<\mathrm{dist}(x,\partial\Omega)<2\sqrt{\varepsilon}$? Or can we even make more layers inside with more scales, as $|u^\varepsilon - u^0| = \mathcal{O}(1)$ is not possible near the boundary $\partial\Omega$.
\end{enumerate}
\color{black}

>>>>

\begin{proof} For $\delta>0$, let us define $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\Omega) < \delta\}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: \mathrm{dist}(x,\overline{\Omega}) < \delta\}$. 
\begin{figure}[ht]
    \centering
    %\incfig{Domains}
    \def\svgwidth{0.47\columnwidth}
    \import{./figs/}{Domains.pdf_tex}
    \caption{The domain $\Omega$ variations $\Omega_\delta, \Omega^\delta$.}
    \label{fig:Domains}
\end{figure}
We consider $\delta$ small enough so that the distance function $x\mapsto \mathrm{dist}(x,\partial \Omega)$ is $\mathrm{C}^2$ in the strip $\Omega^\delta\backslash \overline{\Omega}_\delta$, we recall that $|D d(x)| = 1$ in that region. We extend the signed distance function into a $\mathrm{C}^2(\mathbb{R}^n)$ function, denoted by $d(x)$ such that 
\begin{equation*}
    \begin{cases}
    d(x)\geq 0\;\text{for}\;x\in\Omega\;\text{with}\;d(x) = +\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega\backslash \Omega_\delta,\\
    d(x)\leq 0\;\text{for}\;x\notin \Omega\;\text{with}\;d(x) = -\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega^\delta\backslash \Omega.
    \end{cases}
\end{equation*}
We can choose $d(\cdot)$ so that $\Omega_\delta = \{x\in \mathbb{R}^n: d(x)-\delta >0 \}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: d(x) +\delta>0\}$.

@@

\begin{lem}\label{lem:supersln} For each $\eta>0$ there exists $M_\eta > 0$ such that 
\begin{equation*}
    \overline{w}_{\eta,\delta}(x) = \frac{C_\varepsilon-\eta}{(d(x)+\delta)^\alpha} -\frac{M_\eta}{\lambda}, \qquad x\in \Omega^\delta
\end{equation*}
is a supersolution of \eqref{eq:PDEeps} in $\Omega^\delta$.
\end{lem}

@@

\begin{prop}\label{pro:minimalsol} There exists a minimal solution $\underline{u}\in \mathrm{C}^2(\Omega)$ of \eqref{eq:PDEeps} such that $v\geq \underline{u}$ for any other solution $v\in \mathrm{C}^2(\Omega)$ solving \eqref{eq:PDEeps}.
\end{prop}
\begin{proof} Let $w_{\eta,\delta}\in \mathrm{C}^2(\Omega)$ solves
    \begin{equation}\label{e:w_def}
    \begin{cases}
        \mathcal{L}\left[w_{\eta,\delta}\right] = 0 &\qquad\text{in}\;\Omega,\\
        \qquad w_{\eta,\delta} = \underline{w}_{\eta,\delta} &\qquad\text{on}\;\partial\Omega.
    \end{cases}
    \end{equation}
    Fix $\eta>0$, as $\delta\to 0$ the value of $\underline{w}_{\eta,\delta}$ blows up on the boundary, therefore by comparison principle we have $\delta_1 \leq  \delta_2$ implies $w_{\eta,\delta_1}\leq  w_{\eta,\delta_2}$ on $\overline{\Omega}$.

@@

\section{Rate of convergence via Doubling variables}
\noindent Let $\Omega = B(0,1)$. Let $\sigma \in (0,1)$ and $\beta \in (0,1)$ to be chosen later, let us define
\begin{align*}
    \Phi^{\sigma}(x,y) =  u^\varepsilon(x) - u^0(y) - \frac{|x-y|^2}{\sigma}- \frac{C_\varepsilon}{d(x)^{\alpha+\beta}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}.
\end{align*}
\paragraph{\textcolor{blue}{\textbf{Step 1.}}} Since $u^\varepsilon d(x)^\alpha \to C_\varepsilon$ as $d(x)\to 0$, we see that $\Phi^\sigma(x,y)\to -\infty$ as $d(x)\to 0$, therefore for a fixed $\varepsilon>0$, there is $(x_{\sigma},y_\sigma)\in \Omega\times\overline{\Omega}$ such that 
\begin{equation*}
    \max_{\overline{\Omega}\times \overline{\Omega}} \Phi^\sigma = \Phi^\sigma(x_\sigma,y_\sigma).
\end{equation*}
\paragraph{\textcolor{blue}{\textbf{Step 2.}}} Preliminaries estimates.
\begin{itemize} 
    \item[(a)] $\Phi^\sigma(x_\sigma,y_\sigma) \geq \Phi^\sigma(x_\sigma,x_\sigma)$ gives us that
    \begin{align*}
        u^\varepsilon(x_\sigma) - u^0(y_\sigma) - \frac{|x_\sigma-y_\sigma|^2}{\sigma}- \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+\beta}} \geq u^\varepsilon(x_\sigma) - u^0(x_\sigma) -  \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+\beta}}
    \end{align*}
    which imlies that
    \begin{equation}\label{e:est_sigma}
        \frac{|x_\sigma-y_\sigma|^2}{\sigma} \leq u^0(x_\sigma) - u^0(y_\sigma) \leq \mathfrak{C}|x_\sigma-y_\sigma| \qquad\Longrightarrow\qquad |x_\sigma -y _\sigma|\leq \mathfrak{C}\sigma.
    \end{equation}
    \item[(b)] $\Phi^\sigma(x_\sigma,y_\sigma) \geq \Phi^\sigma(y_\sigma,y_\sigma)$ gives us that
    \begin{align*}
        u^\varepsilon(x_\sigma) - u^0(y_\sigma) - \frac{|x_\sigma-y_\sigma|^2}{\sigma}- \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+\beta}} \geq u^\varepsilon(y_\sigma) - u^0(y_\sigma) -  \frac{C_\varepsilon}{d(y_\sigma)^{\alpha+\beta}}
    \end{align*}
    which implies that
    \begin{equation*}
        \frac{|x_\sigma-y_\sigma|^2}{\sigma} + C_\varepsilon\left(\frac{1}{d(x_\sigma)^{\alpha+\beta}} - \frac{1}{d(y_\sigma)^{\alpha+\beta}}\right) \leq u^\varepsilon(x_\sigma) - u^\varepsilon(y_\sigma) .
    \end{equation*}
    \item[(c)] $\Phi^\sigma(x_\sigma,y_\sigma) \geq \Phi^\sigma(0,0)$ gives us that
    \begin{align*}
        u^\varepsilon(x_\sigma) - u^0(y_\sigma) - \frac{|x_\sigma-y_\sigma|^2}{\sigma}- \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+\beta}} \geq u^\varepsilon(0) - u^0(0) -  C_\varepsilon
    \end{align*}
    and thus 
    \begin{equation*}
         \frac{|x_\sigma-y_\sigma|^2}{\sigma}+ \frac{C_\varepsilon}{d(x_\sigma)^{\alpha+\beta}}  \leq u^\varepsilon(x_\sigma) - u^\varepsilon(0) + u^0(0) - u^0(y_\sigma) + C_\varepsilon.
    \end{equation*}
\end{itemize}

\newpage
\section{New try}

@@

    \Phi^{\sigma}(x,y) =  u^\varepsilon(x) - u_\delta(y) - \mathfrak{C}\frac{|x-y|^2}{\sigma}- \frac{C_\varepsilon}{d(x)^{\alpha+\beta}}, \qquad (x,y)\in \overline{\Omega}\times\overline{\Omega}_\delta

@@

where $\mathfrak{C}$ is the Lipschitz constant of $u^0$, $u_\delta\in \mathrm{C}(\overline{\Omega}_\delta)$ is the state-constraint solution to

@@

The next questions and tasks:
